A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex
Converted languages piechart into one column figure.  Fonts need to be bigger.
Moving figures.

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/natlang-pie}
\caption{Self-reported native language of 3,154 bilingual Turkers.  Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
\label{lang-pie}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce. MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs),which hints at its origins.  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

@@

Several reports examine Mechanical Turk as an economic market \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that its worker population that should represent a diverse set of languages.

@@

%%%%%%%%%%%%%%% HIT UIs %%%%%%%%%%%
\begin{figure}[h]
\centering
\includegraphics[width=3in]{figures/vocabulary_hit_mturk}
\caption{Translation HIT UI}
\label{tranhit}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=3in]{figures/synonyms_hit_mturk}
\caption{Evaluation HIT UI}
\label{synhit}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Survey Design}
The central task in this study was to use Mechanical Turk to create low cost, high quality bilingual dictionaries for over 100 languages in order to test the reliability and breadth of the knowledge of Mechanical Turk's bilingual population.

@@

The dictionary creation task was broken into two steps: a translation HIT and an evaluation HIT. Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  For the translation task, we asked Turkers to translate individual words, showing each word used in the context of three sentences.  Turkers were allowed to mark that they were unable to translate a word. Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.  The known translations were harvested from the titles of English and foreign articles that were linked via Wikipedia's inter-language links.   The task paid \$0.15 for the translation of 10 words.  Each set of 10 words was independently translated by three separate workers.

@@

>>>>

\section{Background and Related Work}

Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce. MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs),which hints at its origins.  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

@@

Several reports examine Mechanical Turk as an economic market \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries \cite{AmazonRequesterTour}.  This suggest that its worker population that should represent a diverse set of languages.

@@

%%%%%%%%%%%%%%% HIT UIs %%%%%%%%%%%
%\begin{figure}[h]
%\centering
%\includegraphics[width=3in]{figures/vocabulary_hit_mturk}
%\caption{Translation HIT UI}
%\label{tranhit}
%\end{figure}
%
%\begin{figure}[h]
%\centering
%\includegraphics[width=3in]{figures/synonyms_hit_mturk}
%\caption{Evaluation HIT UI}
%\label{synhit}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{figures/natlang-pie}
\caption{Self-reported native language of 3,154 bilingual Turkers.  Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
\label{lang-pie}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Survey Design}
The central task in this study was to use Mechanical Turk to create bilingual dictionaries for over 100 languages in order to test Mechanical Turk's bilingual population.

@@

The dictionary creation task was broken into two steps: a translation HIT and an evaluation HIT. 
%Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  
For the translation task, we asked Turkers to translate individual words, showing each word used in the context of three sentences.  Turkers were allowed to mark that they were unable to translate a word. Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.  .   The task paid \$0.15 for the translation of 10 words.  Each set of 10 words was independently translated by three separate workers.

The known translations were harvested from the titles of English and foreign articles that were linked via Wikipedia's inter-language links.
Keeping only pairs such that (1) the English word is present in the WordNet ontology, (2) the article titles were a single word in both English and the foreign language, (3) the English wikipedia page was not a subcategory of person, and (4) the English and the foreign titles were not identical and were not contained as a substring in the other.

@@

That was method for building gold pairs for english-foreign dictionaries for Vocabulary HIT controls.

We used Brown corpus for building synonyms and non-synonyms pairs for Synonyms HIT controls.
It was built using random words from Brown corpora and if it had any synonyms we added them as pair.
For non-synonyms we took two random words from Brown and if they were not in each others synonyms lists we added them as non-synonyms pair.
